The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-11-22 donde.tex
Prepare draft for submission

In the context of pawnbroker lending, we show that forcing people into commitment contracts with a regular repayment structure decreases their (fee-including) financial cost by 20\%, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 20\%.  Using a multi-armed RCT that includes both a voluntary and a forced arm, we illustrate how to point-identify both the Treatment on the Untreated and the Treatment on the Treated.  We find modest selection on gains but nonetheless significant positive benefits of commitment even for those who would not have chosen it.  %The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.

@@

\textbf{Keywords: } Private paternalism, choice, heterogeneous treatment effects, commitment, overconfidence.

@@

Restrictions of choice are often surreptitiously imposed on consumers. Firms limit their worker's freedom by requiring time-consuming progress reports,  schools impose deadlines and pop quizzes, and loan contracts often require monthly repayment. As pointed out by \cite{Laibson2018}, although these choice-restricting mechanisms may be beneficial to firms and clients, they are often disliked by the latter, and therefore ``shrouded'' by firms, i.e. not advertised but nonetheless embedded in products. \cite{Laibson2018} coins the term ``private paternalism'' for cases when restrictions on the freedom of choice is implemented by a firm in a way that advances a client's interests.

Making a case for private paternalism is not easy. It involves comparing the causal effect of forcing a certain product characteristic against the effect of letting people choose it. Because choice may be correlated with unobservables, identifying these two effects is challenging in observational studies.  %This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully 
Moreover, painting a complete picture of the benefits of forcing requires counterfactuals for both choosers and non-choosers alike, since the differential benefit of forcing arises from impacts among those who do not freely choose commitment. While a large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an intention-to-treat (ITT) sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, this literature has rarely addressed the benefits of imposing commitment or its differential impacts on those who would not independently choose commitment.  
%\footnote{Selection on gains has such wide acceptance that economists often impose it in their models} (Although the examples above are plausible, substantiating a case for private paternalism is not easy. It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose on that characteristic. This is not an easy task because a given person wither has or does not have choice, and because choice induces selection, potentially biasing causal estimates. A large behavioral literature has illustrated that allocating borrowers to a commitment-savings product increase savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature does not show that commitment would not be chosen by those that would benefit from it, that is, that the treatment effect on the untreated (TUT) is positive. 
Indeed, selection on gains has such wide acceptance that economists often impose it as a part of Roy models on topics as diverse as migration \citep{borjas1989economic} and job search \citep{lippman1976economics}.
%, and program evaluation \citep{bjorklund1987estimation}. 
In microfinance, a context close to ours, \citep{Murdoch} claim that there exists positive selection, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments. However, they are unable to show that borrowers indeed benefit or that they indeed positively select based on treatment effects.

%Many people have a difficult time accumulating and retaining capital unless they are provided a structure within which to do so.  The behavioral lens on intertemporal financial services has provided critical insights on this problem, suggesting that saving from cash-in-hand is challenging \citep{Ashraf, Pascaline}, that credit may be preferred to savings as a way of accumulating capital simply because credit repayment contracts provide more structure \cite{Murdoch}, and even that the absence of structured financial contracts may be a key barrier preventing the poor from climbing out of poverty \citep{bertrand2004behavioral, collins2009portfolios}.  A large behavioral literature has illustrated that the addition of commitment-style product features improves the ability to accumulate savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters} and to retire debt \citep{Bertrand, heidhues2010exploiting}.  As a consequence, credit markets featuring limited-liability loans such as small-business financing or microfinance typically take a highly structured approach to credit contracts with frequent repayments and reminders as a way of inducing repayment.  As pointed out by \cite{Laibson2018}, because many of these forms of commitment may be desirable to principals but not demanded by agents (or by the right agents), these mechanisms are often ‘shrouded’, meaning that commitment is embedded in products in ways that are not advertised to clients as such.

This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in Mexico in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the lender in the contract stands to gain the most when borrowers default.

Our partner's standard pawn contract gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty. This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.  %When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments. 
To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner that is not obvious to borrowers. Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.

%clients lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}

%In this paper we examine pawn contracts, an understudied form of credit despite their relative ubiquity \citep{carter2012pawnshops}, and a major vehicle through which poor households may dis-accumulate savings.  There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.  In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner, a Mexican pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.

Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of alternative payment structures in pawn repayment contracts. Our control arm illustrates the costs of the status quo contract: fully \emph{43\%} of borrowers default and so lose their pawn as well as any payments made towards principal.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a ``commitment choice'' arm, in which borrowers can opt into a structured repayment contract at the time of taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if that payment is delinquent. This fee serves as a reminder and a means of reinforcing the importance of these interim payments. In addition, we include a ``forced commitment'' arm, in which all borrowers are \emph{required} to repay using the structured monthly contract that is offered on an opt-in basis in the commitment choice arm.

The combination of voluntary and forced commitment within the RCT allows us to address several key questions. First, do structured repayment contracts lower financial costs for pawnshop borrowers? Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely given the presence of a forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment. In particular, we use the choice, control, and forced arms to point identify the Treatment on the Treated (TOT) and the Treatment on the Untreated (TUT) effects, along with the average selection on gains (ASG) and average selection bias (ASB).

Our results suggest that commitment is strongly effective in preventing default in pawnshop lending, with the average individual in the forced arm paying financing costs inclusive of fees that are 20\% lower than the control, while default decreases by 6.5 percentage points (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points. That is, by imposing the structure of commitment it is possible to save borrowers money by charging them fees! These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using each borrower's subjective value of the pawn rather than the appraised value of the gold, and adjusting for lost liquidity from requiring monthly payments.

The monthly payment contract seems to achieve these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not.  By inducing borrowers either to fully recover or to default without making any payments it saves money that would otherwise have been paid towards loans that ultimately default, money which is lost to the borrower.  In the treatment group, the first payment occurs 13 days earlier, and the fraction recovering on the first visit is 7.7 percentage points higher. Commitment contracts also decrease the fraction of borrowers who make a payment but ultimately fail to recover their pawn by 7 percentage points.  Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. That is, the commitment contract induces people who would otherwise pay something towards recovery but default to instead pay more and faster, making them more likely to recover their pawn at a lower financial cost.

In spite of a large average treatment effect documenting financial cost savings, only 11\% of borrowers in the choice arm actually choose commitment. If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. Can the borrowers who did not choose commitment be those who simply don’t need it? We address this question by sequentially imposing more structure on the problem.

We start our analysis of heterogeneity by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distributions in the treatment and control arms as in \cite{fan2010sharp}. We find that at least 24\% of individual borrowers benefit from commitment, implying many borrowers did not demand it even though their individual treatment effect is positive. Next, we impose the exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to that contract.\footnote{This is a frequently used assumption even if often implicit. For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TUT. We then estimate that the financial cost savings of the TUT is large, at \$356 pesos, equivalent to 24 percentage point savings in APR. That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{We estimate a positive TOT that is larger than the TUT, but it is imprecise--this results from the smaller sample size, given that few chose the monthly payment contract--and the hypothesis of TOT=TUT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}  
%We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e. the average selection bias is negative). Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that 86\% of would-be non-choosers would save on financial cost by being assigned to frequent payments. That is, the benefits of imposing a monthly payment are distributed broadly. \hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and TOT benefits for those with XXX.} 
In a final step, we impose a selection-on-observables assumption and use the Causal Random Forest algorithm of \cite{atheygrf} to estimate conditional average treatment effects (both ATEs and TUTs) for the individual borrowers in our experiment.  We estimate that 93\% of the borrowers who did not opt for the commitment contract have positive conditional TUT effects, while only 1\% of those who chose commitment have negative conditional TOT effects.   While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even the random forest only reduces the overall mis-targeting rate from 8\% (all to Forcing) to 5.5\% (our best-case feasible targeting mechanism).

%however those most economically vulnerable, and those most overconfident about their probability of repayment, experience larger gains.

%\footnote{As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.}

%Borrowers assigned to the forced commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.  However, when offered the choice of commitment, very few borrowers elect to commit voluntarily.  Only 10\% of the choice arm takes up the contract, and none of the core study outcomes are significantly improved by the ability to choose commitment.

%This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice versus forcing with a money-metric outcome such as loan repayment.

%Most importantly, our multi-arm design allows us to show that the \textit{wrong} people choose commitment when offered it.   We illustrate this point in three distinct ways.  First, we use a Random Forest algorithm \citep{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.  93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.  Second, a Boosted Classification Algorithm arrives at a similar answer, showing that the borrowers naturally cluster into two groups, one of which is likely to choose commitment and does not benefit from it, and the other the reverse.  Finally, estimating LATEs on compliers and non-compliers alike we show that the estimated treatment effect on non-compliers is larger than the treatment effect on compliers.  That is, those choosing commitment benefit less from commitment than those not choosing it.  Hence our results show clearly that a paternalistic policy forcing borrowers into a more rigid and structured repayment regimen is uniquely beneficial to them.  While this perverse relationship between choice and benefits from commitment echo closely the findings of \cite{Sprenger} we are the first to be able to examine this relationship using a high-stakes, money-metric outcome in a natural field environment.

What explains the persistence of no-commitment contracts so contrary to borrowers’ interests in the real world?  First, we show substantial levels of over-optimism among borrowers. Among borrowers who do not choose it, those with the largest benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.  The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

Does learning eventually overcome the low demand for commitment? 
%For learning to happen clients would need to experiment with the frequent payment contract, and this was not the typical contract in the industry. But even if the contract was experienced, borrower may fail to learn or learn only slowly. 
We find that borrowers who are assigned the forced commitment contract are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract. One potential interpretation of this result is that borrowers who experience the frequent payment contract rationally choose to borrow more later on because of the lower effective financial costs that this contract entails.\footnote{An alternative interpretation is that the monthly payments from the commitment contract sap borrowers liquidity, leading them to take a second loan to pay off the first. This is unlikely because subsequent loans fall outside the 90 day period within which payments for the first loan are due. Moreover, the correlation is also present conditional on having paid down the first loan. Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments. We test this and we cannot reject that demand is higher after experiencing the monthly payment contract, however sample sizes are small and power for this analysis is correspondingly low.
%While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.  Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.  The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.
Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) does not generate adequate demand in this context.

%We hesitate to give precise policy recommendations since we don't have good measures of welfare. Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety. Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate. \hl{Note also that since the fee for skipping payment is 2\%, the iliquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.

%we estimate that over 50\% of the borrowers in our study are naïve hyperbolics in the sense that they would benefit from commitment but will not choose it.  While our results are driven by the intersection of overcollateralization and a potential selection of the borrower pool towards myopia and short-term financial thinking, these attributes are likely to be present in many types of pro-poor financial markets where individuals lack the credit histories to be able to leverage short-term credit without collateral. This suggests that regulators of such markets should include what is paid through equilibrium default as part of the financing cost (not done now), and to consider imposing structured lending products that tilt the scales towards allowing borrowers to repay.  While commitment-style repayment contracts decrease effective liquidity by requiring faster repayment of a given loan, the improvement in expected borrower returns are so substantial as to prove welfare improving at all but the most astronomical discount rates.

>>>>

We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending. Forcing borrowers into commitment contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% inclusive of fees, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%. Leveraging the special features of our experimental design, we go on to point-identify the effects of commitment on both the treated and the untreated simultaneously, along with the average selection on gains. We find large and significant effects of commitment even for borrowers who would not voluntarily choose it, and no evidence of selection on gains: borrowers who would freely choose commitment do not appear to benefit more than borrowers who would not. A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment. %The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.

@@

\textbf{Keywords: } Private paternalism, choice, treatment on the untreated, heterogeneous treatment effects, commitment, overconfidence.

@@

The behavioral finance literature has established an important role for commitment devices in helping consumers to achieve their own financial goals.  While most academic studies on commitment focus on the role of voluntary self-commitment \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, in reality the predominant use of rigid structure in financial services is involuntary; firms only offer a product with these features embedded.  \cite{Laibson2018} has referred to this implicit bundling of commitment devices as ``private paternalism'', and its logic is that individuals may benefit from commitment and yet not explicitly demand it.  Comparing voluntary versus paternalistic programs requires that we form counterfactuals for two different groups of people: those who would freely choose commitment, and those who would not (since the latter group is treated only under paternalist policies). In this paper we present an experimental design and econometric analysis that point-identifies and provides estimates for both the effect of treatment on the treated (TOT) and on the untreated (TUT). This permits a clear window into the case for paternalistic (forced) rather than voluntary commitment in financial services.

The relationship between treatment effects and treatment take-up is a core concern in the econometrics literature. In principle, the Marginal Treatment Effect (MTE) approach allows researchers to use observational data and a single excluded instrument to study this relationship. In practice, however, unless the instrument has a rich support set, MTEs can only be point identified by using additional modeling assumptions \citep{mogstad2018using}. An alternative research strategy to study the relation between treatment effects and treatment take-up uses the Becker-Degroot-Marschak (BDM) mechanism, incentivizing choice prior to treatment assignment to elicit willingness to pay (WTP) for treatment \citep{becker1964measuring}. 
A number of studies, however, find that the WTP elicited under the BDM mechanism changes substantially with the distribution of prices used in the elicitation exercise \citep{bohm1997eliciting,banerji2014detection}. This falsifies the assumption of standard preferences that is required for BDM to be incentive-compatible \cite{mamadehussene2023reliability}, suggesting that the mechanism may not provide a reliable measure of actual compliance  in practice.
Our study avoids the drawbacks of the MTE and BDM approaches by combining a novel three-armed randomized controlled experiment, including forced treatment and treatment choice arms, with two transparent exclusion restrictions. Together, these allow us to point identify the relevant TOT and TUT effects in a real-world, high-stakes setting and to study the case for paternalistic commitment head-on, with minimal assumptions.

We apply this approach to an important and understudied context: pawnshop lending. 
Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For purposes of comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{There is a large literature showing that stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscilate around 15\% (\url{https://tinyurl.com/yc2x5bjf}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent. The fee serves as a reminder and a means of reinforcing the importance of these interim payments. In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.

%The combination of voluntary and forced commitment within the RCT allows us to address several key questions. 
We address three key questions. First, do structured repayment contracts lower financial costs for pawnshop borrowers? Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely, do the \textit{right} borrowers voluntarily demand commitment? Our ability to answer the last question comes from our unique three-armed experimental design, which we call the ``controlled choice design'' for short. This design can be viewed as a juxtaposition of \emph{two} randomized encouragement designs, each with one-sided non-compliance. One of them point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (TOT),
while the other point identifies the effect of commitment for borrowers who would \emph{not} (TUT).
By identifying both the TOT and TUT effects in the same experiment, the controlled choice design allows us to examine the empirical relevance of ``selection on gains'' also known as Roy-type selection into treatment by estimating the ``average selection on gains'' $\text{ASG} = \text{TOT} - \text{TUT}$. This enables us to test whether borrowers who voluntarily choose commitment have higher average treatment effects than those who do not, rather than assuming it. The controlled choice design also point identifies the average selection bias (ASB)--the average difference in untreated (status quo) potential outcomes for those who choose commitment relative to those who do not--along with the average selection on levels (ASL)--the analogous comparison for treated (commitment) potential outcomes. Taken together, these causal effects allow us to ``go under the hood'' of our baseline ATE results, and paint a more complete and economically relevant picture of the effects of commitment. We are unaware of any other paper that simultaneously identifies all of these causal effects without recourse to additional structural modeling assumptions.

We find that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average individual in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing falls by 11 percentage points (19\% of the mean). In short, structured commitment saves borrowers money by charging them fees! Our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit. They are also robust to using borrowers' \emph{subjective} values of their pawns rather than the appraised value of the gold, and to adjusting for lost liquidity from requiring monthly payments.  The monthly payment contract seems to achieve these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not. The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do.

Despite these large financial cost savings, only 11\% of borrowers in the choice arm choose commitment. 
%If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. 
Can the borrowers who did not choose commitment be those who simply don't need it? 
To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
%We address this question by sequentially imposing more structure on the problem. 
We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}. This approach imposes no assumptions beyond the experimental randomization. We find that \textit{at least} 23\% of borrowers benefit from commitment. This implies that there must be many borrowers in the choice arm who did not demand commitment despite their \emph{individual treatment effect} from (forced) commitment being positive. Next, we impose an exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it. In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract. This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}. \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.} 
It also has testable implications that we fail to reject in our empirical context.\footnote{See \ref{append:exclusion} for details.}
Under this restriction, the controlled choice design point identifies the TOT, TUT, ASG, ASB, and ASL effects described above.  Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had. Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATE, using the Causal Random Forest algorithm of \cite{atheygrf}. We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the commitment contract. 
In short, it is extremely difficult to find identifiable groups of borrowers who are \emph{harmed} by commitment, even when restricting attention to those who would not choose it voluntarily. 
%while only 37\% of those who chose commitment have negative conditional TOT effects.
While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even our best random forest targeting only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).

What explains the persistence of no-commitment contracts so contrary to borrowers’ interests in the real world?  From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers. Among borrowers who do not choose commitment, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment without the need to commit, potentially decreasing their demand from commitment. From the supply side, because borrowers' financial savings come directly from the pockets of lenders, pawnshops have an interest in retaining the no-commitment contract.
Indeed, pawnshop lending presents an inverted lending case: since these loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.  Our partner's \emph{status quo} pawn contract gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that could be paid back anytime before the loan comes due at no penalty. This contract is standard contract in the industry. This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.

%By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.

Our paper makes a number of contributions to the literature. First, we propose a way to use this three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers. This difference is what allows our design to point identify the ASG and related quantities.} 
We further provide simple, regression-based estimators for each of these causal parameters, along with procedures for computing associated cluster-robust standard errors.\footnote{See \ref{append:randchoice} for details.} A companion STATA package provides easy-to-use commands that implement our estimators and standard errors. The controlled choice design could be useful in other experimental settings where the question of interest centers on the merits of paternalism, public or private, or the relationship between choice and treatment effects. One obvious example is the design of other financial contracts beyond pawn loans. Another is education, where teachers typically mandate quizzes, homework, and other commitment mechanisms to mitigate student procrastination \citep{Ariely}. 
We further contribute to a relatively small existing literature that sheds light on private paternalism. In the context of food choice, \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment. In contrast to their paper, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection. In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates. He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in. In contrast, our approach point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject.

%This controlled choice design is key to measuring the effects of mandated versus voluntary imposition of product features.  This question is of interest in a large class of cases. Financial contracts frequently feature dimensions of private paternalism, such as mandatory frequent payment structures for loans. But beyond finance, in education, most teachers mandate homework with deadlines to deal with procrastination \citep{Ariely}. In the workplace, firms monitor employee attendance,\footnote{\url{https://www.wsj.com/lifestyle/careers/attention-office-resisters-the-boss-is-counting-badge-swipes-5fa37ff7}.} but also set and monitor time-specific goals. In the public policy domain we have seat belt mandates, age-dependent medical checkups, etc., which often go beyond nudging. Having a rigorous way to estimate the causal effects of mandates vs choice policies ---and not just for the average individual--- is critically important.
%\footnote{The ``LATE-and-reweight'' approach goes beyond LATE by assuming no unobserved selection-on-gains \citep{aronow2013beyond,angrist2013extrapolate}. In our approach, we estimate selection-on-gains directly. Finally, as the MTE literature relies on a combination of instruments with rich support and additional structural assumptions such as additive separability of observed and unobserved determinants of treatment effect heterogeneity \citep{heckman2007econometric, cornelissen2018benefits}. In a returns-to-education setting, \cite{oreopoulos2006estimating} uses a direct approach to identify a LATE.}

%\cite{Walters} takes the latter approach, combining a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates that differ substantially from those implied by a LATE-and-reweight approach.

%\footnote{In a returns-to-education setting, \cite{oreopoulos2006estimating} uses a direct approach to identify a LATE % \emph{nearly} equals a TUT effect: the 1944 Butler Act increased the share of British children who remained in school until age 15 from 43\% to over 90\%. Because 100\% of borrowers in our forced arm are treated, we identify the TUT rather than an approximation to it.}

Our study also speaks to recent research on the effects of payment frequency. While experiments in microfinance markets have \textit{not} shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{Murdoch}. These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default. Second, we provide a deeper analysis of \textit{both} take-up and the efficacy of voluntary commitment mechanisms. A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}. Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it. This allows us to conduct a more rigorous and nuanced analysis of private paternalism.

%By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) does not generate adequate demand in this context.

The remainder of the paper is structured as follows:  Section \ref{context} provides context and defines our main outcome variables. Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms. Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} shows how to identify, estimate and carry out inference for the TOT, TUT, ASG, ASB and ASL effects under the controlled choice design. Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted and Section \ref{conclusion} concludes.
